### 2009-12-01 doc/tech_doc/a-rex/arex_tech_doc.tex
cleaning up and clarifying configuration options

Due to historical reasons configuration of the A-REX is split into
2 parts. The small part is located inside HED configuration (see Appendix~\ref{annex:arex-conf}) for schema and description of supported elements. It refers to
file containing main part of configuration. The default location of
main configuration file is \textit{/etc/arc.conf}.

The configuration file can contain empty lines and comments in lines
starting with \#. It is separated into sections. Each section starts
from string containing pattern

@@

Each section continues till next section or end of file. One configuration
file can have commands for multiple services/modules/programs. Each
service get it's own section named after it. The A-REX uses section
\emph{{[}grid-manager]}. Some services can make use of multiple subsections
to reflect their internal modular structure. Commands in section \emph{{[}common]}
apply to all services. Command lines have format

\begin{shaded}
\verb|name=``arguments string''|
\end{shaded}
Following commands are defined:

\begin{itemize}
\item \textbf{\textit{joblog}}\textit{={[}path]} -- specifies where to store
log file containing information about started and finished jobs.
\item \textbf{\textit{jobreport}}\textit{={[}URL ... number]} -- specifies
that A-REX has to report information about jobs being processed (started,
finished) to centralized service running at given \textit{URL}. Multiple
entries and multiple URLs are allowed. \textit{number} specifies how
long old records have to be kept if failed to be reported. That value
is specified in days. Last specified value becomes effective.
\item \textbf{\textit{jobreport\_credentials}}\textit{={[}key\_file
    {[}cert\_file {[}ca\_dir]]]} -- specifies the credentials for
  accessing the accounting service.
\item \textbf{\textit{jobreport\_options}}\textit{={[}options]}
  -- specifies additional options for Usage Reporter and/or
  accounting service. The \textit{options} string is interpreted by Usage
  Reporter, its format is described in the corresponding technical document.
\item \textbf{\textit{securetransfer}}\textit{=yes|no} -- specifies whether
to use encryption while transferring data. Currently works for GridFTP
only. Default is \emph{no}. It is overridden by value specified in
URL options.
\item \textbf{\textit{passivetransfer}}\textit{=yes|no} -- specifies
  whether GridFTP transfers are passive. Setting this option to yes
  can solve transfer problems caused by firewalls. Default is no.

@@

to yes the A-REX won't initiate download/upload files. Instead it
composes script submitted to LRMS in way to make it do that. This

@@

- specifies maximum number of jobs being processed by the A-REX at

@@

\textit{max\_processed\_jobs} -- maximal amount of jobs being processed
by A-REX. This does not limit amount of jobs, which can be submitted
to A-REX\\
\textit{max\_running jobs} -- maximal amount of jobs passed to Local

@@

\textit{max\_frontend\_jobs} -- maximal amount of jobs heavily using
resources of frontend (applied before moving job to PREPARING and
FINISHING states)\textit{}\\

@@

is used only by PREPARING or by FINISHING jobs aforementioned number
of jobs can be moved to another state. This is used to avoid case
then jobs can't finish due to big amount of recently submitted jobs.\textit{}\\
\textit{max\_transfered\_files} -- maximal number of files being transferred

@@

\emph{plugin} (external executable) to be run every time job is going
to switch to \emph{state}. Following states are allowed: ACCEPTED,

@@

not 0 job is canceled by default. \textit{Options} consist of \textit{name}=\textit{value}
pairs separated by a comma. Following \textit{name}s are supported:\\

@@

data is received for longer than \textit{max\_inactivity} seconds.

@@

that URLs, starting from template should be accessed in a different

@@

-- mostly identical to \textit{copyurl} but file won't be copied. Instead
soft-link will be created. \textit{replacement} specifies the way

@@

is missing, \textit{local\_path} will be used instead. Both \textit{node\_path}
and \textit{replacement} should not be URLs.

@@

has to choose between few URLs from which should it download input

@@

Per UNIX user commands:

\begin{itemize}
\item \textbf{\textit{mail}}\textit{=e-mail\_address} -- specifies an email
address \textbf{from} which the notification mails are sent.
\item \textbf{\textit{defaultttl}}\textit{=ttl {[}ttr]} -- specifies the
time in seconds for the SD to be available after job finished (\emph{ttl})
and after job was deleted (\emph{ttr}) due to \emph{ttl}. Defaults
are 7 days for \emph{ttl} and 30 days for \emph{ttr}.
\item \textbf{\textit{lrms}}\textit{=default\_lrms\_name default\_queue\_name}
- specifies names for the LRMS and queue. Queue name can also be specified
in the JD (currently it is not allowed to override LRMS by usingon
the JD).
\item \textbf{\textit{sessiondir}}\textit{=path} -- specifies path to the directory
in which the SD is created. If the path is {*} the default one is
used -- \textit{\$HOME/.jobs}.
\item \textbf{\textit{cachedir}}\textit{=path {[}link\_path]} - specifies
a directory to store cached data (see section \ref{sec:cache}). Multiple
cache directories may be specified by specifying multiple \emph{cachedir}
commands. Cached files will be distributed evenly between the caches.
Specifying no \emph{cachedir }command or commands with an empty path
disables caching. Optional \textit{link\_path} specifies the path
at which \emph{path} is accessible on computing nodes, if it is different
from the path on the A-REX host. If \textit{link\_path} is set to '.'
files are not soft-linked, nor are per-job links created, but files
are copied to the session directory.
\item \textbf{\textit{cachesize}}\textit{=high\_mark {[}low\_mark]} -
  specifies high and low watermarks for space used on the file system
  on which the cache directory is located, as a percentage of total
  file system capacity. When the max is exceeded, files will be
  deleted to bring the used space down to the min level. It is a good
  idea to have each cache on its own separate file system. To turn off
  this feature, \char`\"{}cachesize\char`\"{} without parameters can
  be specified. These cache settings apply to all caches specified by
  \emph{cachedir} commands.
\item \textbf{\textit{maxrerun}}\textit{=number} -- specifies maximal number
of times job will be allowed to rerun after it failed at any stage.
Default value is \emph{5}. This only specifies a upper limit. Actual
number is provided in job description and defaults to 0.
\end{itemize}

All per-user commands should be put before \textit{control} command
which initiates serviced user.

\begin{itemize}
\item \textbf{\textit{control}}\textit{=path username {[}username {[}...]]}
- This option initiates UNIX user as being serviced by the A-REX.
\textit{path} refers to the control directory (see Section~\ref{section:internals}
for the description of control directory). If the path is {*} the
default one is used -- \verb|$HOME/.jobstatus|. \textit{username} stands
for UNIX name of the local user. Multiple names can be specified.
If the name is {*} it is substituted by all names found in file \texttt{/etc/grid-security/grid-mapfile}
(for the format of this file one should study the Globus project~\cite{globus}).\\
Also the special name '.'(dot) can be used. Corresponding control
directory will be used for \textbf{any} user. This option should be
the last one in the configuration file. There is also command \textbf{\textit{controldir}}\textit{=path}.
It uses special username '.' and is always executed last independent
of placement in file.
\item \textbf{\textit{helper}}\textit{=username command {[}argument {[}argument
{[}...]]]} -- associates external program with the local UNIX user.
This program will be kept running under account of the specified user.
\textit{username} stands for the name of the user. Special names can
be used: '{*}' -- all names from /etc/grid-security/grid-mapfile, '.'
- root user. The user should be already configured with \textit{control}
option (except root, who is always configured). \textit{command} is
an executable and \textit{argument}s are passed as arguments to it.
\end{itemize}

@@

Following are global commands specific to communication with underlying
LRMS (PBS in this case).

@@

\begin{itemize}
\item [{\%R}] -- session root -- see command \emph{session}
\item [{\%C}] -- control dir -- see command \emph{control}
\item [{\%U}] -- username
\item [{\%u}] -- userid -- numerical
\item [{\%g}] -- groupid -- numerical
\item [{\%H}] -- home dir -- home specified in /etc/passwd
\item [{\%Q}] -- default queue -- look command 'defaultlrms'
\item [{\%L}] -- default lrms -- look command 'defaultlrms'
\item [{\%W}] -- installation path -- \$\{ARC\_LOCATION\}
\item [{\%G}] -- globus path -- \$\{GLOBUS\_LOCATION\}
\item [{\%c}] -- list of all control directories
\item [{\%I}] -- job's ID (for plugins only, substituted in runtime)
\item [{\%S}] -- job's state (for \emph{authplugin} plugins only, substituted
in runtime)
\item [{\%O}] -- reason (for \emph{localcred} plugins only, substituted
in runtime). Possible reasons are:
\begin{list}{--}{\setlength{\labelwidth}{0.5cm}\setlength{\rightmargin}{\leftmargin}}
\item [{new}] -- new job, new credentials
\item [{renew}] -- old job, new credentials
\item [{write}] -- write/delete file, create/delete directory
\item [{read}] -- read file, directory, etc.
\item [{extern}] -- call external program 
\end{list}
\end{itemize}

>>>>

Due to historical reasons configuration of the A-REX is split into 2
parts. The small part is located inside HED configuration (see
Appendix~\ref{annex:arex-conf} for schema and description of supported
elements). This configuration refers to the file containing the main
part of the configuration. The default location of the main
configuration file is \textit{/etc/arc.conf}.

The configuration file can contain empty lines and comments in lines
starting with \#. It is separated into sections. Each section starts
with a string containing

@@

Each section continues until the next section or until the end of the
file. The configuration file can have commands for multiple
services/modules/programs. Each service has its own section named
after it. The A-REX uses the \emph{{[}grid-manager]} section. Some
services can make use of multiple subsections to reflect their
internal modular structure. Commands in section \emph{{[}common]}
apply to all services. Command lines have the format

\begin{shaded}
\verb|name=``arguments string''|
\end{shaded}
The following commands are defined:

Commands affecting the A-REX process and logging:

\begin{itemize}
\item \textbf{\textit{pidfile}}\textit{=path} -- specifies file where
  process id of A-REX process will be stored. Defaults to
  \emph{/var/log/arched.pid} if running as root and
  \emph{\$HOME/arched.pid} otherwise.
\item \textbf{\textit{logfile}}\textit{=path} -- specifies name of file
  for logging debug/informational output. Defaults to
  \emph{/var/log/grid-manager.log}.
\item \textbf{\textit{logsize}}\textit{=size number} -- restricts
  log file size to \emph{size} and keeps \emph{number} archived log
  files.
\item \textbf{\textit{debug}}\textit{=number} -- specifies level of
  debug information. More information is printed for higher
  levels. Currently the highest effective number is 5 (DEBUG) and
  lowest 0 (FATAL). Defaults to 2 (WARNING).
\item \textbf{\textit{user}}\textit{=username} -- specifies username to
  which the A-REX must switch after reading configuration. Defaults to
  \emph{not switch}.
\end{itemize}

Commands setting limits and options for how the A-REX handles jobs and
files:

\begin{itemize}
\item \textbf{\textit{joblog}}\textit{=path} -- specifies where to store
log file containing information about started and finished jobs.
\item \textbf{\textit{jobreport}}\textit{=URL ... number} -- specifies
that A-REX has to report information about jobs being processed (started,
finished) to a centralized service running at the given \textit{URL}. Multiple
entries and multiple URLs are allowed. \textit{number} specifies how
long (in days) old records have to be kept if failed to be
reported. The last specified value becomes effective.
\item \textbf{\textit{jobreport\_credentials}}\textit{=key\_file
    {[}cert\_file {[}ca\_dir]]} -- specifies the credentials for
  accessing the accounting service.
\item \textbf{\textit{jobreport\_options}}\textit{=options}
  -- specifies additional options for Usage Reporter and/or
  accounting service. The \textit{options} string is interpreted by Usage
  Reporter, its format is described in the corresponding technical document.
\item \textbf{\textit{securetransfer}}\textit{=yes|no} -- specifies whether
to use encryption while transferring data. Currently works for GridFTP
only. Default is \emph{no}. It is overridden by values specified in
URL options.
\item \textbf{\textit{passivetransfer}}\textit{=yes|no} -- specifies
  whether GridFTP transfers are passive. Setting this option to yes
  can solve transfer problems caused by firewalls. Default is no.

@@

to yes the A-REX will not download/upload files but compose script
submitted to the LRMS in order that the LRMS can execute file tranfer. This

@@

-- specifies maximum number of jobs being processed by the A-REX at

@@

\textit{max\_processed\_jobs} -- maximum number of concurrent jobs
processed by A-REX. This does not limit the amount of jobs, which can
be submitted to the cluster.\\
\textit{max\_running jobs} -- maximum number of jobs passed to Local

@@

\textit{max\_frontend\_jobs} -- maximum number of jobs in PREPARING and
FINISHING states (downloading and uploading files). Jobs in these
states can cause a heavy load on the A-REX host. This limit is applied
before moving jobs to PREPARING and FINISHING states.\\

@@

is used only by PREPARING or by FINISHING jobs, aforementioned number
of jobs can be moved to another state. This is used to avoid the case
where jobs cannot finish due to a large number of recently submitted jobs.\\
\textit{max\_transferred\_files} -- maximum number of files being transferred

@@

\emph{plugin} (external executable) to be run every time job is about
to switch to \emph{state}. The following states are allowed: ACCEPTED,

@@

not 0 job is canceled by default. \textit{Options} consists of \textit{name}=\textit{value}
pairs separated by commas. The following \textit{name}s are supported:\\

@@

data is received for longer than \textit{max\_inactivity} seconds. To
allow statistics to build up, no transfers will be stopped within the
first 3 minutes.

@@

that URLs starting from \emph{template} should be accessed in a different

@@

-- mostly identical to \textit{copyurl} but file will not be copied. Instead
a soft-link will be created. \textit{replacement} specifies the way

@@

is missing, \textit{local\_path} will be used instead. Neither \textit{node\_path}
nor \textit{replacement} should be URLs.

@@

has to choose between several URLs from which should it download input

@@

Per UNIX user commands

\begin{itemize}
\item \textbf{\textit{mail}}\textit{=e-mail\_address} -- specifies an email
address \textbf{from} which notification mails are sent.
\item \textbf{\textit{defaultttl}}\textit{=ttl {[}ttr]} -- specifies the
time in seconds for the SD to be available after job finishes (\emph{ttl})
and after job was deleted (\emph{ttr}) due to \emph{ttl}. Defaults
are 7 days for \emph{ttl} and 30 days for \emph{ttr}. The minumum value
for both parameters is 2 hours.
\item \textbf{\textit{lrms}}\textit{=default\_lrms\_name default\_queue\_name}
-- specifies names for the LRMS and queue. Queue name can also be specified
in the JD (currently it is not allowed to override LRMS by using
the JD).
\item \textbf{\textit{sessiondir}}\textit{=path} -- specifies path to
  the directory in which the SD is created. If \emph{path} is {*} the
  default sessiondir is used -- \textit{\$HOME/.jobs}.
\item \textbf{\textit{cachedir}}\textit{=path {[}link\_path]} -- specifies
a directory to store cached data (see section \ref{sec:cache}). Multiple
cache directories may be specified by specifying multiple \emph{cachedir}
commands. Cached files will be distributed evenly between the caches.
Specifying no \emph{cachedir }command or commands with an empty path
disables caching. Optional \textit{link\_path} specifies the path
at which \emph{path} is accessible on computing nodes, if it is different
from the path on the A-REX host. If \textit{link\_path} is set to '.'
files are not soft-linked, nor are per-job links created, but files
are copied to the session directory.
\item \textbf{\textit{cachesize}}\textit{=high\_mark {[}low\_mark]} --
  specifies high and low watermarks for space used on the file system
  on which the cache directory is located, as a percentage of total
  file system capacity. When the max is exceeded, files will be
  deleted to bring the used space down to the min level. It is a good
  idea to have each cache on its own separate file system. To turn off
  this feature, \char`\"{}cachesize\char`\"{} without parameters can
  be specified. These cache settings apply to all caches specified by
  \emph{cachedir} commands.
\item \textbf{\textit{maxrerun}}\textit{=number} -- specifies maximal number
of times job will be allowed to rerun after it failed at any stage.
Default value is \emph{5}. This only specifies a upper limit. The actual
number is provided in job description and defaults to 0.
\end{itemize}

All per-user commands should be put before the \textit{control} command
which initiates serviced user.

\begin{itemize}
\item \textbf{\textit{control}}\textit{=path username {[}username
    {[}...]]} -- This option initiates UNIX user as being serviced by
  the A-REX.  \textit{path} refers to the control directory (see
  Section~\ref{section:internals} for the description of control
  directory). If the path is {*} the default one is used --
  \verb|$HOME/.jobstatus|. \textit{username} stands for UNIX name of
  the local user. Multiple names can be specified.  If the name is {*}
  it is substituted by all names found in file
  \texttt{/etc/grid-security/grid-mapfile} (for the format of this
  file one should study the Globus project~\cite{globus}).\\ Also the
  special name '.'(dot) can be used. Corresponding control directory
  will be used for \textbf{any} user. This option should be the last
  one in the configuration file. There is also command
  \textbf{\textit{controldir}}\textit{=path}.  It uses special
  username '.' and is always executed last independent of its
  placement in file.
\item \textbf{\textit{helper}}\textit{=username command {[}argument
    {[}argument {[}...]]]} -- associates an external program with the
  local UNIX user.  This program will be kept running under account of
  the user specified by \textit{username}. Special names can be used:
  '{*}' -- all names from /etc/grid-security/grid-mapfile, '.'  - root
  user. The user should be already configured with \textit{control}
  option (except root, who is always configured). \textit{command} is
  an executable and \textit{argument}s are passed as arguments to it.
\end{itemize}

The following are global commands specific to communication with the underlying
LRMS.

@@

@@

\begin{itemize}
\item [{\%R}] -- session root -- see command \emph{sessiondir}
\item [{\%C}] -- control dir -- see command \emph{control}
\item [{\%U}] -- username
\item [{\%u}] -- userid -- numerical
\item [{\%g}] -- groupid -- numerical
\item [{\%H}] -- home dir -- home specified in /etc/passwd
\item [{\%Q}] -- default queue -- see command \emph{lrms}
\item [{\%L}] -- default lrms -- ses command \emph{lrms}
\item [{\%W}] -- installation path -- \$\{ARC\_LOCATION\}
\item [{\%G}] -- globus path -- \$\{GLOBUS\_LOCATION\}
\item [{\%c}] -- list of all control directories
\item [{\%I}] -- job ID (for plugins only, substituted in runtime)
\item [{\%S}] -- job state (for \emph{authplugin} plugins only, substituted
in runtime)
\item [{\%O}] -- reason (for \emph{localcred} plugins only, substituted
in runtime). Possible reasons are:
\begin{list}{--}{\setlength{\labelwidth}{0.5cm}\setlength{\rightmargin}{\leftmargin}}
\item [{new}] -- new job, new credentials
\item [{renew}] -- old job, new credentials
\item [{write}] -- write/delete file, create/delete directory
\item [{read}] -- read file, directory, etc.
\item [{extern}] -- call external program 
\end{list}
\end{itemize}
